\texttt 4-16-17

### 2017-04-17 latex/permutorconstruction/permutations.tex
improved permutation encryption construction

\author{Anonymous\inst{1}}
\institute{City, State \email{address@provider.com}}
\title[\texttt Design date]{\texttt Design date}

@@

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Permutation]{Permutation}\todo{Keywords?}

\begin{abstract}
  We define a permutation with an N\todo{Block size?}-bit block size. The design is oriented towards PLATFORM TYPE\todo{Constrained Devices? Consumer CPUs? What architecture/native word sizes?}. The design makes use of certain instruction types or gates. \todo{XOR/AND? ADD/XOR? Multiplication? Modular Exponentiation? Lookup Tables?}\\ 
\end{abstract}

@@

\todo{Explain the motivation for the design described here}

\section{Definitions}
\todo{Define the notation used in this paper}\\
\todo{Define how the state is laid out and indexed/addressed}\\
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left...

\section{Algorithm}
\todo{Define the algorithm in detail}\\
\todo{Describe the layout of the state}\\
\todo{Define the round function or permutation}

>>>>

\author{Ella Rose\inst{1}}
\institute{Paso Robles, CA\email{python_pride@protonmail.com}}
\title[\texttt 4-16-17]{\texttt 4-16-17}

@@

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Permutation, Cipher Construction, AEAD]{Permutation, Cipher Construction, AEAD}\todo{Keywords?}

\begin{abstract}
 We define a permutation based construction for providing single pass authenticated encryption of data. Our specific definition recommends a 512-bit permutation and a 256-bit key to encrypt a 256-bit block of data. Our construction is very simple and easy to implement; It should be significantly less code then a block cipher with a mode of operation and HMAC. It is generic, and can be instantiated with any psuedorandom permutation.
\end{abstract}

@@

In this work we present a construction that utilizes a psuedorandom permutation to create a simple streaming authenticated encryption system.

\section{Definitions}
\todo{Define the notation used in this paper}\\
\todo{Define how the state is laid out and indexed/addressed}\\
We use $\oplus$ to denote XOR and $||$ to denote concatenation.

\section{Algorithm}
\begin{Algorithmic}
\Function{$encrypt$}{$data, key, iv$}
	\State $k \gets key$
	\For{
